\textbf{{\Large {Recursive algorithm for the computation of branching coefficients of affine Lie algebras with applications in CFT}}}

### 2009-12-16 AffineLieAlgebras/InformalNotes/article.tex
Added one paper to the bibliography

All the cases are listed in the following table.
\begin{figure}[ph]
\label{fig:table}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of the algebra $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\  
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{figure}
In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.

>>>>

All the cases are listed in the table \ref{tab:diagrams}.
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of the algebra $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\  
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}
In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.
